Predicting Ambient Air Pollution (PM2.5) Across the Contiguous U.S.

### 2023-04-23 Draft.Rmd
Update Draft.Rmd

### 4. Random FOrest Regression

>>>>

### 4. Random FOrest Regression
The Random Forest (RF) Regression model performs by training multiple different samples simultaneously and averages the outcome at the end for the final prediction. The randomness of these samples contribute to the prediction accuracy of this model. Similar to the XG Boosting Regression model, we preprocess the training set with the same features to improve make the predictive modeling process and then create model specifications. This processed data is assigned to 'folds4' and resampled on 5 subsets of the training set. We tune the hyperparameters to make the modeling process more efficient and perform grid specification to determine which hyperparameter values have high prediction accuracy (i.e. low prediction error). Next, we isolated the best hyperparameter values, so they can be used for the final boosting model. Lastly, we fitted the model and evaluated its prediction performance. Its RMSE score was .62, indicating the RF is a good predictive model.
